Exploiting Non-Slip Wall Contacts to Position\\ Two Particles Using The Same Control Input

### 2019-01-04 journalWallFriction/SwarmShapeControl.tex
Added pictures and refs, shrank to 12 pages

%\usepackage{wrapfig}
\usepackage{overpic}
%\usepackage{subfigure}
%\usepackage{textcomp}
\graphicspath{{./pictures/pdf/},{./pictures/ps/},{./pictures/png/},{./pictures/jpg/}}
\usepackage{breqn} %for breaking equations automatically
\usepackage[ruled]{algorithm}
\usepackage{algpseudocode}
%\usepackage{algorithmic}
\usepackage{multirow}
\usepackage{todonotes}
\usepackage{authblk}
\usepackage[per-mode=symbol, detect-weight=true, binary-units=true]{siunitx}
\usepackage{rotating}
\usepackage{tikz}
\usepgflibrary{arrows}% for more options on arrows
%\newcommand{\todo}[1]{\vspace{5 mm}\par \noindent \framebox{\begin{minipage}[c]{0.98 \columnwidth} \ttfamily\flushleft \textcolor{red}{#1}\end{minipage}}\vspace{5 mm}\par}
% uncomment this to hide all red todos
%\renewcommand{\todo}{}

@@

% You will get a Paper-ID when submitting a pdf file to the conference system
\author{Shiva Shahrokhi,~\IEEEmembership{Member,~IEEE,} Jingang Shi,  Benedict Isichei, and Aaron T. Becker,~\IEEEmembership{Senior Member,~IEEE,}% <-this % stops a space
\thanks{*This work was supported by the National Science Foundation under Grant No.\ \href{http://nsf.gov/awardsearch/showAward?AWD_ID=1553063}{ [IIS-1553063]}, \href{http://nsf.gov/awardsearch/showAward?AWD_ID=1619278}{[IIS-1619278]}, and  \href{https://nsf.gov/awardsearch/showAward?AWD_ID=1646566}{[CNS-1646566]}.}% <-this % stops a space
\thanks{Authors are with the Department of Electrical and Computer Engineering,  University of Houston, Houston, TX 77204 USA        {\tt\small  \{sshahrokhi2,atbecker\}@uh.edu}}%
\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
%\affil{Department of Electrical and Computer Engineering, \\
% University of Houston, Houston, TX 77204-4005 USA\\
% {\tt\small  \{sshahrokhi2, aviswanathanmahadev, atbecker\}@uh.edu}}
%\thanks{S. Shahrokhi, A. Mahadev and  A. Becker are with the Department of Electrical and Computer Engineering,  University of Houston, Houston, TX 77204-4005 USA {\tt\small  \{sshahrokhi2, aviswanathanmahadev, atbecker\}@uh.edu}
%}
%} %\end thanks
\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
{Shahrokhi \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}

@@

%%%%%%%%%%%%%%%
\input{intro}
%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
\input{relatedWork}
%%%%%%%%%%%%%%%
\input{theory}
\input{theory2robAlgs}
%\input{theorynrobAlgs}
%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
\input{simulation}
%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
\input{experiment}
%%%%%%%%%%%%%%%
\input{conclusion}
%%%%%%%%%%%%%%%
%\section*{Acknowledgments}
%%%%%%%%%%%%%%%
%% Use plainnat to work nicely with natbib. 
{%\footnotesize
%\bibliographystyle{plainnat}
%\bibliographystyle{SageH}
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,SwarmShapeControl}
}
%Shiva Shahrokhi, Jingang Shi,  Benedict Isichei, and Aaron T. Becker
%
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{shiva.jpg}}]{Shiva Shahrokhi}(S`14) received M.S. and PhD degrees in the Electrical and Computer Engineering Department at the University of Houston in 2018.  
She received the B.S. degree in Computer Engineering from Iran University of Science and Technology,
Tehran, Iran. She is involved in studies of swarm manipulation and control for robotics applications.
These include steering massively under-actuated mobile robotic ensembles, swarm shape control, and machine learning.
\end{IEEEbiography}
%
\begin{IEEEbiography}{Jingang Shi}
Biography text here.
\end{IEEEbiography}
%
\begin{IEEEbiography}{Benedict Isichei}
received an M.S. degree in the Electrical and Computer Engineering Department at the University of Houston in 2018.
\end{IEEEbiography}
%
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{DrB.jpg}}]{Aaron T. Becker}(S`06-M`12-SM`17) received M.S. and PhD degrees in electrical and computer engineering from the University of Illinois at Urbana-Champaign, in 2008 and 2012. He was a post doctoral research scholar at the Multi-Robot Systems Lab at Rice University and at Boston Children's Hospital \& Harvard Medical School, before joining the Electrical and Computer Engineering Department at the University of Houston as an Assistant Professor in 2014. He won the best paper at IROS 2013 and received the NSF CAREER award in 2016. %He is active in developing control laws and algorithms for robot swarms.
\end{IEEEbiography}

\end{document}

>>>>

%\usepackage{wrapfig}
\usepackage{overpic}
%\usepackage{subfigure}
%\usepackage{textcomp}
\graphicspath{{./pictures/pdf/},{./pictures/ps/},{./pictures/png/},{./pictures/jpg/}}
\usepackage{breqn} %for breaking equations automatically
\usepackage[ruled]{algorithm}
\usepackage[noend]{algpseudocode}
%\usepackage{algorithmic}
\usepackage{multirow}
\usepackage{todonotes}
\usepackage{authblk}
\usepackage[per-mode=symbol, detect-weight=true, binary-units=true]{siunitx}
\usepackage{rotating}
\usepackage{tikz}
\usepgflibrary{arrows}% for more options on arrows
%\newcommand{\todo}[1]{\vspace{5 mm}\par \noindent \framebox{\begin{minipage}[c]{0.98 \columnwidth} \ttfamily\flushleft \textcolor{red}{#1}\end{minipage}}\vspace{5 mm}\par}
% uncomment this to hide all red todos
%\renewcommand{\todo}{}

@@

% You will get a Paper-ID when submitting a pdf file to the conference system
\author{Shiva Shahrokhi,~\IEEEmembership{Member,~IEEE,} Jingang Shi,  Benedict Isichei, and Aaron T. Becker,~\IEEEmembership{Senior Member,~IEEE}% <-this % stops a space
\thanks{*This work was supported by the National Science Foundation under Grant No.\ \href{http://nsf.gov/awardsearch/showAward?AWD_ID=1553063}{ [IIS-1553063]}, \href{http://nsf.gov/awardsearch/showAward?AWD_ID=1619278}{[IIS-1619278]}, and  \href{https://nsf.gov/awardsearch/showAward?AWD_ID=1646566}{[CNS-1646566]}.}% <-this % stops a space
\thanks{Authors are with the Department of Electrical and Computer Engineering,  University of Houston, Houston, TX 77204 USA        {\tt\small  \{sshahrokhi2,atbecker\}@uh.edu}}%
\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
%\affil{Department of Electrical and Computer Engineering, \\
% University of Houston, Houston, TX 77204-4005 USA\\
% {\tt\small  \{sshahrokhi2, aviswanathanmahadev, atbecker\}@uh.edu}}
%\thanks{S. Shahrokhi, A. Mahadev and  A. Becker are with the Department of Electrical and Computer Engineering,  University of Houston, Houston, TX 77204-4005 USA {\tt\small  \{sshahrokhi2, aviswanathanmahadev, atbecker\}@uh.edu}
%}
%} %\end thanks
\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
{Shahrokhi \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}

@@

%%%%%%%%%%%%%%%
\input{intro}
%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
\input{relatedWork}
%%%%%%%%%%%%%%%
\input{theory}
\input{theory2robAlgs}
%\input{theorynrobAlgs}
%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
\input{simulation}
%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
\input{experiment}
%%%%%%%%%%%%%%%
\input{conclusion}
%%%%%%%%%%%%%%%
%\section*{Acknowledgments}
%%%%%%%%%%%%%%%
%% Use plainnat to work nicely with natbib. 
{%\footnotesize
%\bibliographystyle{plainnat}
%\bibliographystyle{SageH}
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,SwarmShapeControl}
}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{shiva.jpg}}]{Shiva Shahrokhi}(S`14) received M.S. and PhD degrees in the Electrical and Computer Engineering Department at the University of Houston in 2018.  
She received the B.S. degree in Computer Engineering from Iran University of Science and Technology,
Tehran, Iran. She is involved in studies of swarm manipulation and control for robotics applications.
These include steering massively under-actuated mobile robotic ensembles, swarm shape control, and machine learning.
\end{IEEEbiography}
%
\vspace{-1em}
\begin{IEEEbiography}
[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{JingangShi.jpg}}]{Jingang Shi}
Jingang Shi received the B.Eng. degree in the School of Materials Science and Engineering at Huazhong University of Science and Technology in 2018. 
 He studied robot control during a four-month internship at the University of Houston in 2017.
 He is studying for the M.E. degree in the School of Mechanical Science and Engineering at Huazhong University of Science and Technology.
\end{IEEEbiography}
%
\vspace{-1em}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Benedict.jpg}}]{Benedict Isichei}
received an M.S. degree in the Electrical and Computer Engineering Department at the University of Houston in 2018. 
 His thesis was titled ``Robotic Manipulators: Cryogenic Magnetic Manipulation System, Two-body Magnetic Manipulation, and Low-cost Robotic Manipulators'', and features low cost robotics. See his designs at https://www.thingiverse.com/Bisichei.
\end{IEEEbiography}
%
\vspace{-1em}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{DrB.jpg}}]{Aaron T. Becker}(S`06-M`12-SM`17) received M.S. and PhD degrees in electrical and computer engineering from the University of Illinois at Urbana-Champaign, in 2008 and 2012. He was a post doctoral research scholar at the Multi-Robot Systems Lab at Rice University and at Boston Children's Hospital \& Harvard Medical School, before joining the Electrical and Computer Engineering Department at the University of Houston as an Assistant Professor in 2014. He won the best paper at IROS 2013 and received the NSF CAREER award in 2016. %He is active in developing control laws and algorithms for robot swarms.
\end{IEEEbiography}
%
\end{document}

### 2019-01-04 journalWallFriction/simulation.tex
Added pictures and refs, shrank to 12 pages

%  This equation can be simplified to 
% 
% \begin{equation}
%\sqrt{1+s^2-2 s \cos \theta}+  \sqrt{1+e^2-2 e \cos(\beta-\theta)}. 
% \end{equation}
% 
\begin{figure}
\centering
\renewcommand{\figwid}{\columnwidth}
{\begin{overpic}[width =\figwid]{shortestpath3.pdf}
\end{overpic}
}
\caption{\label{fig:shortestpath}{The shortest path between two points $S$ to $E$ in the unit disk that intersects the circumference. The path length as a function of intersection point, $P= (\cos\theta,\sin\theta)$ is shown at right. See \cite{BeckerShortestPath}.}
%\vspace{-1em}
}
\end{figure}

@@

\begin{overpic}[width=0.67\columnwidth]{Move4.pdf}\put(55.5,32.5){\begin{turn}{50.5} 
{\begin{tikzpicture}[thick]
\draw [red,   -  , dotted      ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{Move5.pdf}\put(55.5,32.5){\begin{turn}{50.5} 
{\begin{tikzpicture}[thick]
\draw [red,   -   , dotted     ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{finalMove.pdf}\end{overpic}
\caption{\label{fig:reachableSet}
Frames from reconfiguring two particles. 
Top six images show a polygonal workspace and the corresponding $\Delta$ configuration space with its 2-move reachable sets. 
Bottom six images show a disk-shaped workspace and the corresponding $\Delta$ configuration space with its 2-move reachable sets. 
For each, moves 1 and 3 are simple translations of both particles and so the reachable sets do not change.
The reachable set morphs during move 2 because one particle is held stationary by the boundary. 
See multimedia attachment for animations of each.
}
\end{figure*}

%\subsection{Position Control of Two Robots}
\begin{figure}
\centering
\begin{overpic}[width=0.49\columnwidth]{middlegoalnum.pdf}\put(0,75){a)}\end{overpic}
\begin{overpic}[width=0.49\columnwidth]{middlegoaldist.pdf}\put(0,75){b)}\end{overpic}
\begin{overpic}[width=0.49\columnwidth]{worstnum.pdf}\put(0,75){c)}\end{overpic}
\begin{overpic}[width=0.49\columnwidth]{worstdist.pdf}\put(0,75){d)}\end{overpic}
\caption{\label{fig:contour}
%Plots show performance with one goal on the boundary.
Circular workspace: contour plots showing the number of moves and distance commanded if red particle's goal position is varied in $x$ and $y$. 
Starting positions of red and blue particles  
 (\protect\tikz \protect\draw[red,fill=white,line width=0.3mm] (-1ex,0) rectangle (0,1ex);,
 \protect\tikz \protect\draw[blue,fill=white,line width=0.3mm] (-1ex,0) rectangle (0,1ex);)
 and goal position of blue particle  \protect\tikz \protect\draw[blue,fill=white,line width=0.3mm] (0,0) circle (.5ex); are fixed.
The top row has the blue particle's goal position  at the origin, generating symmetric contour plots.
Moving the  blue particles' goal position  to $(-0.2,0)$, generates non-symmetric contour plots.
}
\end{figure}

@@

\begin{figure}
\centering
\renewcommand{\figwid}{1\columnwidth}
{
\begin{overpic}[width =\figwid]{contourDistnew.png}\put(-2,10){\begin{turn}{90} \tiny{unique particles}
\end{turn}}
%
\end{overpic}
\vspace{1em}
\begin{overpic}[width =\figwid]{JustSimulationV6.png}\put(-2,10){\begin{turn}{90} \tiny{unique particles}
\end{turn}}
%
\end{overpic}
\begin{overpic}[width =\figwid]{identical.png}\put(-2,6){\begin{turn}{90} \tiny{interchangeable particles}
\end{turn}}
\end{overpic}
}\caption{\label{fig:contourPlots}{Square workspace: starting positions of particles $1$ and $2$ 
 (\protect\tikz \protect\draw[blue,fill=white,line width=0.3mm] (-1ex,0) rectangle (0,1ex);,
 \protect\tikz \protect\draw[myMagenta,fill=white,line width=0.3mm] (-1ex,0) rectangle (0,1ex);)
and goal position of particle $2$ (\protect\tikz \protect\draw[myMagenta,fill=white,line width=0.3mm] (0,0) circle (.5ex);) are fixed, and $\epsilon=0.001$.
 The top row of contour plots show the distance if particle $1$'s goal position is varied in $x$ and $y$. The middle row shows the number of moves required for the same configurations. The bottom row shows the same configuration but when the particles are interchangeable.}
\vspace{-1em}
}
\end{figure}
Algorithm \ref{alg:optimalAlg}  was implemented in Mathematica using particles with zero radius. Figure \ref{fig:reachableSet} shows frames of the algorithm in two representative workspaces, square and disk, with two arbitrary starting and goal configurations.
%An online interactive demonstration and source code of the algorithm are available at \cite{Shahrokhi2015mathematicaParticle}.
%  Fig.~\ref{fig:shapeControlMathematica1}  shows  an implementation of this algorithm with robot initial positions represented by hollow squares and final positions by circles. 
 %Dashed lines show the shortest route if robots could be controlled independently, while solid lines show the optimal shortest  path using uniform inputs.

>>>>

%  This equation can be simplified to 
% 
% \begin{equation}
%\sqrt{1+s^2-2 s \cos \theta}+  \sqrt{1+e^2-2 e \cos(\beta-\theta)}. 
% \end{equation}
% 
\begin{figure}
\centering
\renewcommand{\figwid}{\columnwidth}
{\begin{overpic}[width =\figwid]{shortestpath3.pdf}
\end{overpic}
}
 \vspace{-1em}
\caption{\label{fig:shortestpath}{The shortest path between two points $S$ to $E$ in the unit disk that intersects the circumference. The path length as a function of intersection point, $P= (\cos\theta,\sin\theta)$ is shown at right. See \cite{BeckerShortestPath}.}
%\vspace{-1em}
}
\end{figure}

@@

\begin{overpic}[width=0.67\columnwidth]{Move4.pdf}\put(55.5,32.5){\begin{turn}{50.5} 
{\begin{tikzpicture}[thick]
\draw [red,   -  , dotted      ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{Move5.pdf}\put(55.5,32.5){\begin{turn}{50.5} 
{\begin{tikzpicture}[thick]
\draw [red,   -   , dotted     ] (1,14.0) -- (0,14.0);
\end{tikzpicture}}\end{turn}}\end{overpic}
\begin{overpic}[width=0.67\columnwidth]{finalMove.pdf}\end{overpic}
\vspace{-1em}
\caption{\label{fig:reachableSet}
Frames from reconfiguring two particles. 
Top six images show a polygonal workspace and the corresponding $\Delta$ configuration space with its 2-move reachable sets. 
Bottom six images show a disk-shaped workspace and the corresponding $\Delta$ configuration space with its 2-move reachable sets. 
For each, moves 1 and 3 are simple translations of both particles and so the reachable sets do not change.
The reachable set morphs during move 2 because one particle is held stationary by the boundary. 
See multimedia attachment for animations of each.
}
\end{figure*}

%\subsection{Position Control of Two Robots}
\begin{figure}
\centering
\begin{overpic}[width=0.49\columnwidth]{middlegoalnum.pdf}\put(0,75){a)}\end{overpic}
\begin{overpic}[width=0.49\columnwidth]{middlegoaldist.pdf}\put(0,75){b)}\end{overpic}
\begin{overpic}[width=0.49\columnwidth]{worstnum.pdf}\put(0,75){c)}\end{overpic}
\begin{overpic}[width=0.49\columnwidth]{worstdist.pdf}\put(0,75){d)}\end{overpic}
\vspace{-1em}
\caption{\label{fig:contour}
%Plots show performance with one goal on the boundary.
Circular workspace: contour plots showing the number of moves and distance commanded if red particle's goal position is varied in $x$ and $y$. 
Starting positions of red and blue particles  
 (\protect\tikz \protect\draw[red,fill=white,line width=0.3mm] (-1ex,0) rectangle (0,1ex);,
 \protect\tikz \protect\draw[blue,fill=white,line width=0.3mm] (-1ex,0) rectangle (0,1ex);)
 and goal position of blue particle  \protect\tikz \protect\draw[blue,fill=white,line width=0.3mm] (0,0) circle (.5ex); are fixed.
The top row has the blue particle's goal position  at the origin, generating symmetric contour plots.
Moving the  blue particles' goal position  to $(-0.2,0)$, generates non-symmetric contour plots.
}
\end{figure}

@@

\begin{figure}
\centering
\renewcommand{\figwid}{1\columnwidth}
{
\begin{overpic}[width =\figwid]{contourDistnew.png}\put(-2,10){\begin{turn}{90} \tiny{unique particles}
\end{turn}}
%
\end{overpic}
\vspace{1em}
\begin{overpic}[width =\figwid]{JustSimulationV6.png}\put(-2,10){\begin{turn}{90} \tiny{unique particles}
\end{turn}}
%
\end{overpic}
\begin{overpic}[width =\figwid]{identical.png}\put(-2,6){\begin{turn}{90} \tiny{interchangeable particles}
\end{turn}}
\end{overpic}
}\vspace{-1em}
\caption{\label{fig:contourPlots}{Square workspace: starting positions of particles $1$ and $2$ 
 (\protect\tikz \protect\draw[blue,fill=white,line width=0.3mm] (-1ex,0) rectangle (0,1ex);,
 \protect\tikz \protect\draw[myMagenta,fill=white,line width=0.3mm] (-1ex,0) rectangle (0,1ex);)
and goal position of particle $2$ (\protect\tikz \protect\draw[myMagenta,fill=white,line width=0.3mm] (0,0) circle (.5ex);) are fixed, and $\epsilon=0.001$.
 The top row of contour plots show the distance if particle $1$'s goal position is varied in $x$ and $y$. The middle row shows the number of moves required for the same configurations. The bottom row shows the same configuration but when the particles are interchangeable.}
\vspace{-1em}
}
\end{figure}
Algorithm \ref{alg:optimalAlg}  was implemented in Mathematica using particles with zero radius. Figure \ref{fig:reachableSet} shows frames of the algorithm in two representative workspaces, square and disk, with two arbitrary starting and goal configurations.
%An online interactive demonstration and source code of the algorithm are available at \cite{Shahrokhi2015mathematicaParticle}.
%  Fig.~\ref{fig:shapeControlMathematica1}  shows  an implementation of this algorithm with robot initial positions represented by hollow squares and final positions by circles. 
 %Dashed lines show the shortest route if robots could be controlled independently, while solid lines show the optimal shortest  path using uniform inputs.
